{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex

@@

	\section{Application}\label{Application}
		The application uses the methods from the previous sections to predict the octane ratings of the introduced gasoline dataset. The simulation study will contribute towards the reading of the results. 
		\begin{itemize}
			\item {\color{green} incorporate results of simulation study: 					number of basis, components, etc...}
			\item point out difficulties estimating sderror
			\item describe setup and results
		\end{itemize}

>>>>

	Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \citep{Dattoli_2001})

	Adress numerical instability?

	maybee both in paragraph under results instead of here?

@@

	\section{Application}\label{Application}
		The application uses the methods from the previous sections to predict the octane ratings of the introduced gasoline dataset.
		Although the simulation study granted valuable insights in the different methods in the four different settings, it is not enough for determining the method and choice of basis of the application since there is still too much uncertainty involved. To point out some sources of uncertainty: First, we do not know the true coefficient function. The insights from just two functions, $f_1$ and $f_2$, is not enough to draw any conclusion. Second, we do not know anything about the signal-to-noise ratios of the octane rating. Third, we made assumptions about the distribution of $\tilde{\xi}$ that are not relate-able to this real-life application where we not know this distribution. We will run all specification again for the gasoline dataset, but the results from the simulation study will contribute towards the reading of the results. The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 10 fold cross-validation. In total, we conducted 1000 repetitions for each setting.
		\begin{itemize}
			\item {\color{green} incorporate results of simulation study: 					number of basis, components, etc...}
			\item point out difficulties estimating sderror
			\item describe setup and results
		\end{itemize}
	\subsection{Interpretation of Results}
